Supplementary Analysis

### 2017-01-22 doc/paper/supplementary.tex
Finishing methods; edit consistency/simplicity throughout

The model dynamics for the leaky, competing accumulator (LCA) are given as follows:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
        x_i &\rightarrow \max(x_i, 0) .
    \end{split}
\end{equation}
We now justify our choice of $k = \beta = 1$ from the text.
This guarantees that the winning state will converge to its input value, and each losing state will converge to zero.

@@

Setting $\beta = k = 1$, and defining $\chi := \sum_{j} x_j$, we rewrite the dynamics as:
\begin{equation} \label{eq:um-special}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - \chi \right) \frac{1}{\tau} \\
        x_i &\rightarrow \max(x_i, 0) .
    \end{split}
\end{equation}
We conceptualize $\chi$ as a single `meta state-variable' that, based on the value of each $\rho_i$, will change each corresponding $x_i$.
% For instance, we know that $\chi > \rho_i \iff \frac{{\partial x}_i}{\partial t} < 0$.
% This tells us that all $x_i$ will decrease until they are bounded by $0 \le x_i \le \rho_i$.
For instance, if $i$ is the index of the winner, then $x_i$ is necessarily only stable when $\chi = \rho_i \iff \frac{{\partial x}_i}{\partial t} = 0$.
Assuming stability, $\chi = \rho_i > \rho_j$ for all $j \ne i$, and thus each $x_j$ necessarily has a negative derivative.
Consequently, all losers $x_j$ will decrease to 0 and stabilize there due to rectification (and then $\chi = \rho_i = x_i$ holds as anticipated).

@@

The model dynamics for the independent accumulator (IA) are given as follows:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_{1,i}}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j} \right) \frac{1}{\tau_2} \\
        x_{1,i} &\rightarrow \max(x_{1,i}, 0) ,
    \end{split}
\end{equation}
where $\bar{x}_{2, i} := \Theta(x_{2,i} - \vartheta)$ is defined by the Heaviside function shifted by $\vartheta$.
We now justify our choice of $\bar{\beta} = 2$ from the text. % Fixing $\lambda = 1$, $\tau_1 = \tau_2$.

@@

Suppose index $i$ is a loser.
We know that $\bar{x}_{2,i} \le 1$, and $\sum_{j \ne i} \bar{x}_{2,j} \ge 1$, since the Heaviside is bounded above by 1, and some other $j \ne i$ has surpassed its threshold by becoming the winner.
Thus,
\begin{align}
 \frac{{\partial x}_{1,i}}{\partial t} \le \lambda \rho_i \frac{1}{\tau_1} + \left( 1 - \bar{\beta} \right) \frac{1}{\tau_2} < 0 \quad \iff \quad \bar{\beta} > 1 + \lambda \max_i\{\rho_i\} \frac{\tau_2}{\tau_1} ,
\end{align}
which implies that we must enforce the latter condition on $\bar{\beta}$ in order to ensure that all losers go to zero. 
In the text, $\lambda = 1$, $\tau_1 = \tau_2$, and $\max_i\{\rho_i\} < 1$ $\implies \bar{\beta} = 2$ will suffice.

>>>>

The model dynamics for the leaky, competing accumulator (LCA) are given as follows:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
        x_i &\ge 0 .
    \end{split}
\end{equation}
We now justify our choice of $k = \beta = 1$ from the text.
This guarantees that the winning state will converge to its input value, and each losing state will converge to zero.

@@

Setting $\beta = k = 1$, and defining $\chi := \sum_j x_j$, we rewrite the dynamics as:
\begin{equation} \label{eq:um-special}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - \chi \right) \frac{1}{\tau} \\
        x_i &\ge 0.
    \end{split}
\end{equation}
We conceptualize $\chi$ as a single `meta state-variable' that, based on the value of each $\rho_i$, will change each corresponding $x_i$.
% For instance, we know that $\chi > \rho_i \iff \frac{{\partial x}_i}{\partial t} < 0$.
% This tells us that all $x_i$ will decrease until they are bounded by $0 \le x_i \le \rho_i$.
For instance, if $i$ is the index of the winner, then $x_i$ is necessarily only stable when $\chi = \rho_i \iff \frac{{\partial x}_i}{\partial t} = 0$.
Assuming stability, $\chi = \rho_i > \rho_j$ for all $j \ne i$, and thus each $x_j$ necessarily has a negative derivative.
Consequently, all losers $x_j$ will decrease to 0 and stabilize there due to rectification (and then $\chi = \rho_i = x_i$ holds as anticipated).

@@

The model dynamics for the independent accumulator (IA) are given as follows:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} \\
        x_i &\ge 0 ,
    \end{split}
\end{equation}
where $\bar{x}_i := \Theta(x_i - \vartheta)$ is defined by the Heaviside function $\Theta$ shifted by $\vartheta$.
We now justify our choice of $\bar{\beta} = 2$ from the text. % Fixing $\lambda = 1$, $\tau_1 = \tau_2$.

@@

Suppose index $i$ is a loser.
We know that $\bar{x}_i \le 1$, and $\sum_{j \ne i} \bar{x}_j \ge 1$, since the Heaviside is bounded above by 1, and some other $j \ne i$ has surpassed its threshold by becoming the winner.
Thus,
\begin{align}
 \frac{{\partial x}_i}{\partial t} \le \lambda \max_i\{\rho_i\} \frac{1}{\tau_1} + \left( 1 - \bar{\beta} \right) \frac{1}{\tau_2} < 0 \quad \iff \quad \bar{\beta} > 1 + \lambda \max_i\{\rho_i\} \frac{\tau_2}{\tau_1} ,
\end{align}
which implies that it suffices to enforce the latter condition on $\bar{\beta}$ in order to ensure that all losers go to zero. 
In the text, $\lambda = 1$, $\tau_1 = \tau_2$, and $\max_i\{\rho_i\} < 1$ $\implies \bar{\beta} = 2$ is sufficient.
